Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-16 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@86 db7c848b-7755-4df2-b763-8796797afa52

In this systems paper, we present an overview of the integration of research and
commercial developments into the Equalizer parallel rendering framework first
presented in \cite{EMP:09}. While individual research using the system has been
presented since, many important features have not previously been published and
are presented here. In particular, the integration of parallel rendering
research, APIs for developing complex distributed applications, and many
individual features make Equalizer an unique, open source framework to develop
visualization applications for any type of setup and use case.

>>>>

In this systems paper, we present an overview of the integration of research and
commercial developments into the Equalizer parallel rendering framework first
presented in \cite{EMP:09}. While individual research using the system has been
presented since, many important features have not previously been published and
are presented here. In particular, the integration of parallel rendering
research, APIs for developing complex distributed applications, and many
individual features make Equalizer a unique, open source framework to develop
visualization applications for any type of setup and use case.
